Chain separation distribution in protein contact networks

### 2020-08-04 paper/main.tex
Updates from Overleaf

\begin{figure}[h]
    \centering
    \includegraphics[width=0.7\columnwidth]{figures/Fig1.pdf}
    \caption{a) The sequence separation distribution is defined as the separation along the chain (blue) of two connected units (red). b) The solid blue link prohibits some connections from node $A$ (dotted red), while others are still permitted (dotted blue). Counting all newly excluded links, we find that a link of length $k$ prohibits $2(l-1)$ links of length $l$ up to a maximum of $k$ and $2(k-1)$ links of length $k$ or more.}
    \label{fig:schematic}
\end{figure}

@@

>>>>

\begin{figure}[h]
    \centering
    \includegraphics[width=0.7\columnwidth]{figures/FigFig1.pdf}
    \caption{a) The sequence separation distribution is defined as the separation along the chain (blue) of two connected units (red). b) The solid blue link prohibits some connections from node $A$ (dotted red), while others are still permitted (dotted blue). Counting all newly excluded links, we find that a link of length $k$ prohibits $2(l-1)$ links of length $l$ up to a maximum of $k$ and $2(k-1)$ links of length $k$ or more.}
    \label{fig:schematic}
\end{figure}

@@

Protein chain lengths in the PDB vary from small fragments of less than 10 amino acids to large agglomerates of over 2000 residues. The most frequently occurring chain lengths, however are between 100 and 400 residues as shown in Fig.~\ref{fig:pdb_stats}. For the analysis of our theoretical results, we have thus chosen ............ structures of around 200, ........ structures of around 300 and .......... structures of around 400 residues.
